\actualTitle

### 2024-02-16 paperAndPoster/paper.tex
trouble with bibliography
feat: inserted paper bibliography into poster

\documentclass[letterpaper]{article}
\usepackage[top=1in, bottom=1.25in, inner=1.25in, outer=1.25in]{geometry}
\usepackage[style=authoryear-comp]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{float}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{xurl}

\title{Using Bayesian Regression to Quantify Sexual Dimorphism in Dinosaurs}
\author{Eric Campbell \\ \texttt{eric.robert.campbell@gmail.com}}
\date{}
\begin{document}
\maketitle

\newcommand{\species}[1]{\textit{#1}}
\newcommand{\tyran}{\species{Tyrannosaurus rex}{}}
\newcommand{\psit}{\species{Psittacosurus lujiatunensis}{}}
\newcommand{\maia}{\species{Maiasaura peeblesorum}{}}
\newcommand{\normal}[2]{\ensuremath{\mathcal{N}\left(#1, #2\right)}}

@@

\begin{align*}
\text{Length}_{m/f,i} &\sim \normal{\mu_{m/f, i}}{\sigma} \\
\mu_{m/f, i} &= \text{von Betlananffy}(\text{age}_i, L_{ m/f }, A_{ m/f }, K_{ m/f }) \\
L_{ m/f } &\sim \normal{\text{population L}}{0.5} \\
A_{ m/f } &\sim \normal{\text{population A}}{0.025} \\
K_{ m/f } &\sim \normal{\text{population K}}{0.05} \\
\sigma_{m/f} &\sim \normal{0.25}{0.05} \\
\end{align*}

>>>>

\documentclass[letterpaper]{article}
\usepackage[top=1in, bottom=1.25in, inner=1.25in, outer=1.25in]{geometry}
\usepackage[style=authoryear-comp]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{float}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{booktabs}
\input{common.tex}

\title{\actualTitle}
\author{Eric Campbell \\ \texttt{eric.robert.campbell@gmail.com}}
\date{}
\begin{document}
\maketitle

@@

\begin{align*}
\text{Length}_{m/f,i} &\sim \normal{\mu_{m/f, i}}{\sigma_{m / f}} \\
\mu_{m/f, i} &= \text{von Bertalanffy}(\text{age}_i, L_{ m/f }, A_{ m/f }, K_{ m/f }) \\
L_{ m/f } &\sim \normal{\text{population L}}{0.5} \\
A_{ m/f } &\sim \normal{\text{population A}}{0.025} \\
K_{ m/f } &\sim \normal{\text{population K}}{0.05} \\
\sigma_{m/f} &\sim \normal{0.25}{0.05} \\
\end{align*}
